\addcontentsline{toc}{section}{\refname}
\begin{thebibliography}{99}
    \bibitem{olbrich} \selectlanguage{english}  Giant photocurrents in a Dirac fermion system at cyclotron resonance~/ P.~Olbrich [et~al]~// Phys.~Rev.~B, 2013.~--- V.~87.
    \bibitem{hyart} \textbf{Hyart,~T.} Model of the influence of an external magnetic field on the gain of terahertz radiation from semiconductor superlattices~/ T.~Hyart, J.~Mattas, K. N. Alekseev~// Phys.~Rev.~Lett., 2009.~--- V.~103.
    \bibitem{neg-conductivity} \textbf{Kryuchkov,~S.~V.} Possibility of the effect of absolute negative conductivity in quantum superlattice exposed to the high-frequency electromagnetic radiation~/ S.~V.~Kryuchkov, E.~I.~Kukhar~// Superlattice Microst., 2015.~--- V.~83.~--- P.~322.
    \bibitem{mutual-rectification} Mutual Rectification of Alternating Currents in Graphene in the Field of Two Electromagnetic Waves~/ V.~I.~Konchenkov [et~al]~// Phys.~Wave Phen., 2013.~--- V.~21.~--- \No~1.~--- P. 56.
    \bibitem{liu} \textbf{Liu,~R.~B.} Nonlinear optics of semiconductors under an intense terahertz field~/ R.~B.~Liu, B.~F.~Zhu~// Phys.~Rev.~B, 2003.~--- V.~68.~--- P.~195-206.
    \bibitem{attaccalite} \textbf{Attaccalite,~C.} Nonlinear optics from an ab initio approach by means of the dynamical Berry phase: Application to second-and third-harmonic generation in semiconductors~/ C.~Attaccalite, M.~Grüning~// Phys.~Rev.~B, 2013.~--- V.~88.
    \bibitem{silveirinha} \textbf{Silveirinha,~M.} Giant nonlinearity in zero-gap semiconductor superlattices~/ M. Silveirinha, N.~Engheta~// Phys.~Rev.~B, 2014.~--- V.~89.
    \bibitem{mensah} \selectlanguage{russian}  \textbf{Менса,~С.} Взаимное выпрямление двух электромагнитных волн в сверхрешётке~/ С.~Менса, Г.~М.~Шмелев, Э.~М.~Эпштейн~// Известия вузов. Физика, 1988.~--- Т.~31.~--- \No~6.~--- С.~112--114.
    \bibitem{hendry} Coherent Nonlinear Optical Response of Graphene~/ E.~Hendry [et~al]~// Phys.~Rev.~Lett., 2010.~--- V.~105.
    \bibitem{kumar} Third harmonic generation in graphene and few-layer graphite films~/ N.~Kumar [et~al]~// Phys.~Rev.~B, 2013.~--- V.~87.
    \selectlanguage{english}
    \bibitem{two-axis-sl} \textbf{Konchenkov,~V.~I.} Influence of a transverse electric field on the alternating currents rectification effect in superstructures with nonadditive energy spectrum~/ V.~I.~Konchenkov, S.~V.~Kryuchkov, D.~V.~Zav’yalov~// Journal Of Nano- And Electronic Physics, 2013.~--- V.~5.~--- \No~4.
    \selectlanguage{russian}
    \bibitem{gsl-sio2-sic} \textbf{Завьялов,~Д.~В.} Выпрямление поперечного тока в сверхрешетке на основе графена~/ Д.~В.~Завьялов, В.~И.~Конченков, С.~В.~Крючков~// Физика и техника полупроводников, 2012.~--- Т.~46.~--- \No1.~--- С.~113--120.
    \bibitem{feldmann} \selectlanguage{english}  Optical investigation of Bloch oscillations in a semiconductor superlattice~/ J.~Feldmann [et~al]~// Phys.~Rev.~B, 1992.~---V.~46.
    \bibitem{sibille} Observation of Esaki-Tsu negative differential velocity in GaAs/AlAs superlattices~/ A.~Sibille [et~al]~// Phys.~Rev.~Lett., 1990.~--- V.~64.~--- \No~52.
    \bibitem{andronov} \selectlanguage{russian} Транспорт в сверхрешетках со слабыми барьерами и проблема терагерцового блоховского генератора~/  А.~А.~Андронов [и др.]~// УФН, 2003.~--- Т.~173.~--- \No~7.~--- С.~780--783.
    \bibitem{elesin} \textbf{Елесин,~В.~Ф.} Лазер на ``штарковской лестнице'' с когерентной электронной подсистемой~/ В.~Ф.~Елесин, Ю.~В.~Копаев~// УФН, 2003.~--- Т.~173.~--- \No~7.~--- С.~776--780.
    \bibitem{suris} \selectlanguage{english}  \textbf{Suris,~R.~A.} Prospects for quantum dot structures applications in electronics and optoelectronics~/ R.~A.~Suris~// Future Tends in Microelectronics, 1996.~--- P.~197--208.
    \bibitem{bouchard} \textbf{Bouchard,~A.~M.} Semiconductor superlattices as terahertz generators~/ A.~M.~Bouchard, M.~Luban~// Phys.~Rev.~B, 1993.~--- V.~47.
    \bibitem{martini} Superradiant emission from Bloch oscillations in semiconductor superlattices~/ R.~Martini [et~al]~// Phys.~Rev.~B, 1996.~--- V.~54.
    \bibitem{keay} Photon-Assisted Electric Field Domains and Multiphoton-Assisted Tunneling in Semiconductor Superlattices~/ B.~J.~Keay [et~al]~// Phys.~Rev.~Lett.,1995.~--- V.~75.~--- P.~4098--4102.
    \bibitem{dmitriev} \selectlanguage{russian}  \textbf{Дмитриев,~И.~А.} Локализация электронов и блоховские осцилляции в сверхрешетках из квантовых точек в постоянном электрическом поле~/ И.~А.~Дмитриев, Р.~А.~Сурис~// ФТП, 2001.~--- Т.~35.~--- \No. 2.~--- С.~219--226.
    \bibitem{suris-dmitriev} \textbf{Сурис,~Р.~А.} Блоховские осцилляции в сверхрешетках из квантовых точек~/ Р.~А.~Сурис, И.~А.~Дмитриев~// УФН, 2003.~--- Т.~173.~--- \No~7.~--- С.~769--776.
    \bibitem{esaki} \selectlanguage{english} \textbf{Esaki,~L.} Superlattice and negative differential conductivity in semiconductors~/ L.~Esaki, R.~Tsu~// IBM J.~Res.~and Dev., 1970.~--- V.~14.~--- \No~1.~--- P.~61--67.
    \bibitem{mensah1} \textbf{Mensah,~S.~Y.} Effect of ionization of impuritycentres by electric field on the conductivity of superlattice~/ S.~Y.~Mensah, F.~Allotey, A.~Clement~// Phys.~1C, 1994.~--- P.~335--342.
    \bibitem{ktitorov} \selectlanguage{russian}  \textbf{Ктиторов,~С.~А.} Влияние брэгговских отражений на высокочастотную проводимость электронной плазмы твердого тела~/ С.~А.~Ктиторов, Г.~С.~Симин, В.~Я.~Синдаловский~// ФТТ, 1971.~--- Т.~13.~--- \No~8.~--- C.~2230-2233.
	\bibitem{alekseev} \selectlanguage{english}  Spontaneous dc Current Generation in a Resistively Shunted Semiconductor Superlattice Driven by a Terahertz Field~/ K.~N.~Alekseev [et~al]~// Phys.~Rev.~Lett., 1998.~--- V.~80.~--- P.~2669--2672.
    \bibitem{shmelev} \selectlanguage{russian}  \textbf{Шмелев,~Г.~М.} Фотостимулированный четный акустоэлектрический эффект~/ Г.~М.~Шмелев, Г.~И.~Цуркан, Нгуен Хог Шон~// Изв.~вузов.~Физика, 1985.~--- No 2.~--- С.~84--88.
    \bibitem{unterrainer} \selectlanguage{english}  Inverse Bloch oscillator: strong terahertz-photocurrent resonances at the Bloch frequency~/ K.~Unterrainer [et~al]~// Phys.~Rev.~Lett, 1996.~--- V.~76.~--- \No~16.~--- P.~2973--2976.
    \bibitem{mensah2} \textbf{Mensah,~S.~Y.} Effect of high frequency field on the transport properties of superlattice~/ S.~Y.~Mensah~// J.~Phys.: Condensed Matter, 1992.~--- V.~4.~--- P.~362--369.
	\bibitem{bass} \textbf{Bass,~F.~G.} Large-amplitude electromagnetic waves in conductors with a nonparabolic charge carrier dispersion law~/ F.~G.~Bass, L.~B.~Vatova~// Phys Rep.~1994.~--- V.~241.~--- P.~219.
	\bibitem{ghosh} \textbf{Ghosh,~A.~W.} Nonlinear THz response of a one-dimensional superlattice~/ A.~W.~Ghosh, J.~W.~Wilkins~// Phys.~Rev.~B, 2000.~--- V.~61.~--- \No~8.~--- P.~5423-5430.
    \bibitem{red} \selectlanguage{russian}  \textbf{Рыжий,~В.~И.} Абсолютная отрицательная проводимость, индуцированная микроволновым излучением и состояния с нулевым сопротивлением в двумерных электронных системах: история и современное состояние~/ В.~И.~Рыжий~// УФН, 2005.~--- Т.~175.~--- \No~2.~--- С.~205--213.
    \bibitem{pavlovich} \textbf{Павлович,~В.~В.} Проводимость полупроводника со сверхрешеткой в сильных электрических полях~/ В.~В.~Павлович, Э.~М.~Эпштейн~// ФТП, 1976.~--- Т.~10.~--- \No~10.~--- С.~2001.
    \bibitem{sivashova} \textbf{Завьялов,~Д.~В.} Радиоэлектрический эффект в сверхрешетке при воздействии сильного электрического поля~/ Д.~В.~Завьялов, С.~В.~Крючков, Е.~С.~Сивашова~// ПЖТФ, 2006.~--- Т.~32.~--- \No~4.~--- С.~11--15.
    \bibitem{bulgakov} \textbf{Булгаков,~А.~А.} Нелинейное взаимодействие волн в полупроводниковой сверхрешетке~/ А.~А.~Булгаков, О.~В.~Шрамкова~// ФТП, 2001.~--- Т.~35.~--- \No~5.~--- С.~578--585.
    \bibitem{kechiev} \textbf{Игнатов,~А.~А.} Самоиндуцированная прозрачность в полупроводниках со сверхрешеткой~/ А.~А.~Игнатов, Ю.~А.~Романов~// ФТТ, 1975.~--- Т.~17.~--- \No~11.~--- С.~3388--3389.
    \bibitem{goychuk} \selectlanguage{english}  \textbf{Goychuk,~I.} Nonadiabatic Quantum Brownian Rectifiers~/ I.~Goychuk, M.~Grifoni, P.~Hanggi~// Phys.~Rev.~Lett., 1998.~--- V.~81.~--- P.~649--652.
    \bibitem{ratnikov} \selectlanguage{russian}  \textbf{Ратников,~П.~В.} Сверхрешётка на основе графена на полосчатой подложке~/ П.~В.~Ратников~// Письма в ЖЭТФ, 2009.~--- Т.~90.~--- \No~6.~--- С.~515-520.
    \selectlanguage{english}
    \bibitem{novoselov-geim} Electric field effect in atomically thin carbon films~/ K.~S.~Novoselov [et~al]~// Science, 2004.~--- V.~306.~--- P.~666.
    \bibitem{cnoidal-and-sinusoidal} \textbf{Kryuchkov,~S.~V.} Mutual Rectification of Cnoidal and Sinusoidal Electro\-magnetic Waves with Orthogonal Polarization Planes in a Graphene-Based Superlattice~/ S.~V.~Kryuchkov, E.~I.~Kukhar’~// Optics and Spectroscopy, 2012.~--- V.~112.~--- \No~6.~--- P.~914--919.
    \bibitem{kogan} \selectlanguage{russian}  \textbf{Коган,~М.~Н.} Динамика разреженного газа (кинетическая теория)~/ М.~Н.~Коган~--- Москва: Наука, 1967.~--- 440 с.
    \bibitem{graphene-numeric} \textbf{Завьялов,~Д.~В.} Численное моделирование эффекта выпрямления тока, индуцированного электромагнитной волной в графене~/ Д.~В.~Завьялов, С.~В.~Крючков, Т.~А.~Тюлькина~// Физика и техника полупроводников, 2010.~--- Т.~44.~--- \No~7.
\end{thebibliography}

